Milestone 2: Feature Selection - Nearest Neighbors, Logit w/Linear Propensity Score

### 2019-10-28 perf_release_criteria/milestone_3/feature_selection_nn_logit_linear.Rmd
Updating nn logit linear with interactions.

>>>>

# FS 1 Interactions

Feature selection on only performance metrics, but including interaction terms.

```{r fs1_int, error=TRUE}
res_fs1 <- list()
for (bt in names(bts)){
  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, workers = 10, add_interactions=TRUE,
                                      replace=TRUE, distance = 'linear.logit')
}
save.image(results_file_path)
print(res_fs1)
```

```{r fs1_int_noreplace, error=TRUE}
res_fs1_noreplace <- list()
for (bt in names(bts)){
  res_fs1_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, add_interactions=TRUE,
                                                replace=FALSE, workers = 10, distance = 'linear.logit')
}
save.image(results_file_path)
print(res_fs1_noreplace)
```

Performance metrics and the highest found by Boruta with original dataset, but including interaction terms

```{r fs2_int, error=TRUE}
res_fs2 <- list()
for (bt in names(bts)){
  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, add_interactions=TRUE,
                                      replace=TRUE, workers = 10, distance = 'linear.logit')
}
save.image(results_file_path)
print(res_fs2)
```

Never completed after 2.5 days. Killed it...
